### 2023-03-20 paper/main.tex
updates to paper

\urlstyle{same}
\usepackage{wrapfig}

@@

\newpage
\subsection{Describe in detail two use cases using the activity diagram. Choose the most complex use cases.}
\begin{enumerate}
    \item The main use case for the feedback gatherer includes: 
    \begin{enumerate}
        \item Creating a survey after registering
        \item Viewing statistics and responses to an existing survey
        \item Viewing the QR code for the survey they created
    \end{enumerate}
    \hfill \break

    \begin{figure}[h]
        \centering
        \includegraphics[width=0.65\textwidth]{feedbackGatherer.png}
        \caption{Feedback Gatherer Activity Diagram}
    \end{figure}
\newpage
    \item The main use case for the respondent includes:
    \begin{enumerate}
        \item Scanning the QR code to access the survey previously created by the feedback gatherer
        \item Enter responses to the given survey questions
        \item Submit the completed survey
    \end{enumerate}
    \linebreak
    \hfill \break
    \begin{figure}[h]
    \centering
    \includegraphics[width=0.70\textwidth]{respondent.png}
    \caption{Respondent Activity Diagram}
    \end{figure}

@@

Similar to the MVC architecture, the views in Django’s MVT architecture are the dependent objects while the models are the independent objects. In our application, the observer pattern can be used to manage the relationship between the views and the models by notifying the different views whenever there are changes in the model’s data. This can be useful since there are multiple views that are affected by the changes in the data. For example, when a user adds or deletes a survey, this change would be reflected in the survey model. All of the views related to this model would be notified of these changes. The user profile template would display the addition or the deletion of a survey while a new survey page template would be created or deleted. The observer model can be useful in maintaining consistency between the related objects and keeping them up to date. 
\newline
\hfill \break
\textbf{Factory Patterns}

@@

\linebreak
    \hfill \break

\newpage
\subsection{Provide the class diagram of the whole system by incorporating the two design patterns.}
\linebreak
    \hfill \break
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Software Construction}
\subsection{Submit the screenshot of the entire structure of the code within the web framework.}
\linebreak
    \hfill \break

\subsection{Deployment diagram regarding the hardware configuration of the code. Indicate the supported Web browsers, the application/Web servers and the database solution.}
\linebreak
    \hfill \break

\subsection{Screenshots of all table contents of the system data.}
\linebreak
    \hfill \break

\subsection{GitHub link of the entire program. All students must contribute equally to the programming part. The commit log of each student will be checked within GitHub. Website builders, such as Wordpress, are not allowed.}
\linebreak
\url{https://github.com/zachary-huber/feedback-app}
\hfill \break

@@

\section{Acceptance Testing: select test cases for both user roles. The sign-in and sign-up are excluded from testing.}
\subsection{Correctness testing using four test cases (screenshots of both inputs and outputs).}
\newline

\textbf{Feedback gatherer:}
\begin{itemize}
    \item[] Input: Feedback gatherer creates a survey by selecting the types of answers and entering the questions.

Output: When they click the “Create Survey” button, a QR code is generated.

Input: Feedback gatherer clicks on one of the past surveys.

Output: Feedback gatherer can view the responses to the correct survey.
\end{itemize}

\hfill \break
\textbf{Respondent:}
\begin{itemize}
    \item[] Input: Respondent scans the QR code.
    \item[] Output: Respondent is taken to the correct survey.
    \item[] Input: Respondent completes the survey and clicks submit.
    \item[] Output: Respondent is taken to the thank you page.
\end{itemize}

@@

\begin{itemize}
    \item[] Input: Feedback gatherer tries to go to the sign up page while already logged in.

Output: Feedback gatherer is redirected to landing page.

Input: Feedback gatherer tries to go to the login page while already logged in.

Output: Feedback gatherer is redirected to landing page.
\end{itemize}
\newline 
\hfill \break

\textbf{Respondent:}
\begin{itemize}
    \item[] Input: Respondent tries to go the landing page while not logged in.

Output: Respondent is redirected to login page.

Input: Respondent tries to go the create survey page while not logged in.

Output: Respondent is redirected to login page.

>>>>

\urlstyle{same}
\usepackage{wrapfig}
\usepackage{multicol}

\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Java,
  aboveskip=0mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}

@@

\newpage
\subsection{Describe in detail two use cases using the activity diagram. Choose the most complex use cases.}
\begin{enumerate}
    \item The main use case for the feedback gatherer includes: 
    \begin{enumerate}
        \item Creating a survey after registering
        \item Viewing statistics and responses to an existing survey
        \item Viewing the QR code for the survey they created
    \end{enumerate}

    \begin{figure}[h]
        \centering
        \includegraphics[width=0.55\textwidth]{feedbackGatherer2.png}
        \caption{Feedback Gatherer Activity Diagram}
    \end{figure}
\newpage
    \item The main use case for the respondent includes:
    \begin{enumerate}
        \item Scanning the QR code to access the survey previously created by the feedback gatherer
        \item Enter responses to the given survey questions
        \item Submit the completed survey
    \end{enumerate}
    \linebreak

    \begin{figure}[h]
    \centering
    \includegraphics[width=0.70\textwidth]{respondent2.png}
    \caption{Respondent Activity Diagram}
    \end{figure}

@@

Similar to the MVC architecture, the views in Django’s MVT architecture are the dependent objects while the models are the independent objects. In our application, the observer pattern can be used to manage the relationship between the views and the models by notifying the different views whenever there are changes in the model’s data. This can be useful since there are multiple views that are affected by the changes in the data. For example, when a user adds or deletes a survey, this change would be reflected in the survey model. All of the views related to this model would be notified of these changes. The user profile template would display the addition or the deletion of a survey while a new survey page template would be created or deleted. The observer model can be useful in maintaining consistency between the related objects and keeping them up to date. 
\newline
\clearpage

\begin{figure}[h]
        \centering
        \includegraphics[width=0.75\textwidth]{AuthUserClass.png}
        \caption{AuthUser Class}
\end{figure}

\begin{lstlisting}
AuthUser Data Algorithm

interface class Subject
{
	protected observerList: array of Observer
	public void register(Observer)
	public void unregister(Observer)
	public void notify()
}
class AuthUser Data implements Subject
{
	private int is_superuser, is_staff, is_active
	private string password, last_login, username, first_name, last_name, email, date_joined
	public void register(Observer obs)
		observerList.add(obs)
	public void unregister(Observer obs)
		observerList.delete(obs)
	public void notify()
		for each obs in observerList
			obs.update(is_superuser, is_staff, is_active, password, last_login, username, first_name, last_name, email, date_joined)
	public void sendAuthUser() //calls notify()
	public type getState()
		return subjectState
}

interface class Observer
{
	public void update(int, int, int, string, string, string, string, string, string, string)
}
class authUser implement Observer
{
	private int is_superuser, is_staff, is_active
	private string password, last_login, username, first_name, last_name, email, date_joined
	public void update(int is_superuserX, int is_staffX, int is_activeX, astring passwordX, string last_loginX, string usernameX, string first_nameX, string last_nameX, string emailX, string date_joinedX)
	{
		is_superuser = is_superuserX
		is_staff = is_staffX
		is_active = is_activeX
		password = passwordX
		last_login = last_loginX
		username = usernameX
		first_name = first_nameX
		last_name = last_nameX
		email = emailX
		date_joined = date_joinedX
		displayView()
	}
	public void displayView()
}
\end{lstlisting}
\clearpage

\begin{figure}[h]
        \centering
        \includegraphics[width=0.85\textwidth]{ResponsesData.png}
        \caption{Responses Data}
    \end{figure}

\begin{lstlisting}
Responses Data Algorithm

interface class Subject
{
	protected observerList: array of Observer
	public void register(Observer)
	public void unregister(Observer)
	public void notify()
}
class ResponsesData implements Subject
{
	private int response_id, form_id, user_id
	private string response_json, created_at, updated_at
	public void register(Observer obs)
		observerList.add(obs)
	public void unregister(Observer obs)
		observerList.delete(obs)
	public void notify()
		for each obs in observerList
			obs.update(response_id, form_id, user_id, response_json, created_at, updated_at)
	public void sendResponse() //calls notify()
	public type getState()
		return subjectState
}

interface class Observer
{
	public void update(int, int, int, string, string, string)
}
class deleteForm implement Observer
{
	private int response_id, form_id, user_id
	private string response_json, created_at, updated_at
	public void update(int response_idX, int form_idX, int user_idX, string response_jsonX, string created_atX, string updated_atX)
	{
		response_id = response_idX
		form_id = form_idX
		user_id = user_idX
		response_json = response_jsonX
		created_at = created_atX
		updated_at = updated_atX
		displayView()
	}
	public void displayView()
}
class saveResponses implement Observer
{
	private int response_id, form_id, user_id
	private string response_json, created_at, updated_at
	public void update(int response_idX, int form_idX, int user_idX, string response_jsonX, string created_atX, string updated_atX)
	{
		response_id = response_idX
		form_id = form_idX
		user_id = user_idX
		response_json = response_jsonX
		created_at = created_atX
		updated_at = updated_atX
		displayView()
	}
	public void displayView()
}
class results implement Observer
{
	private int response_id, form_id, user_id
	private string response_json, created_at, updated_at
	public void update(int response_idX, int form_idX, int user_idX, string response_jsonX, string created_atX, string updated_atX)
	{
		response_id = response_idX
		form_id = form_idX
		user_id = user_idX
		response_json = response_jsonX
		created_at = created_atX
		updated_at = updated_atX
		displayView()
	}
	public void displayView()
}
\end{lstlisting}

\clearpage
\begin{figure}[h]
        \centering
        \includegraphics[width=0.85\textwidth]{FormsData.png}
        \caption{Forms Data}
    \end{figure}

\begin{lstlisting}
Forms in Projects Application Algorithm

interface class Subject
{
	protected observerList: array of Observer
	public void register(Observer)
	public void unregister(Observer)
	public void notify()
}
class FormsData implements Subject
{
	private int form_id, user_id, is_active
	private string title, description, created_at, updated_at, form_json
	public void register(Observer obs)
		observerList.add(obs)
	public void unregister(Observer obs)
		observerList.delete(obs)
	public void notify()
		for each obs in observerList
			obs.update(form_id, user_id, is_active, title, description, created_at, updated_at, form_json)
	public void sendForms() //calls notify()
	public type getState()
		return subjectState
}

interface class Observer
{
	public void update(int, int, int, string, string, string, string, string)	
}
class survey implement Observer
{
	private int form_id, user_id, is_active
	private string title, description, created_at, updated_at, form_json
	public void update(int form_idX, int user_idX, int is_activeX, string titleX, string descriptionX, string created_atX, string updated_atX, string form_jsonX)
	{
		form_id = form_idX
		user_id = user_idX
		is_active = is_activeX
		title = titleX
		description = descriptionX
		created_at = created_atX
		updated_at = updated_atX
		form_json = formjsonX
		displayView()
	}
	public void displayView()
}
class saveFormEditor implement Observer
{
	private int form_id, user_id, is_active
	private string title, description, created_at, updated_at, form_json
	public void update(int form_idX, int user_idX, int is_activeX, string titleX, string descriptionX, string created_atX, string updated_atX, string form_jsonX)
	{
		form_id = form_idX
		user_id = user_idX
		is_active = is_activeX
		title = titleX
		description = descriptionX
		created_at = created_atX
		updated_at = updated_atX
		form_json = formjsonX
		displayView()
	}
	public void displayView()
}
class deleteForm implement Observer
{
	private int form_id, user_id, is_active
	private string title, description, created_at, updated_at, form_json
	public void update(int form_idX, int user_idX, int is_activeX, string titleX, string descriptionX, string created_atX, string updated_atX, string form_jsonX)
	{
		form_id = form_idX
		user_id = user_idX
		is_active = is_activeX
		title = titleX
		description = descriptionX
		created_at = created_atX
		updated_at = updated_atX
		form_json = formjsonX
		displayView()
	}
	public void displayView()
}
class results implement Observer
{
	private int form_id, user_id, is_active
	private string title, description, created_at, updated_at, form_json
	public void update(int form_idX, int user_idX, int is_activeX, string titleX, string descriptionX, string created_atX, string updated_atX, string form_jsonX)
	{
		form_id = form_idX
		user_id = user_idX
		is_active = is_activeX
		title = titleX
		description = descriptionX
		created_at = created_atX
		updated_at = updated_atX
		form_json = formjsonX
		displayView()
	}
	public void displayView()
}
\end{lstlisting}

\clearpage
\textbf{Factory Patterns}

@@

\linebreak
    \hfill \break
\clearpage
\begin{figure}[h]
        \centering
        \includegraphics[width=0.75\textwidth]{FactoryAuthUser.png}
        \caption{AuthUser Class}
\end{figure}

\begin{lstlisting}
class AuthUserSimpleFactory
{
	public AuthUser createAuthUser(string type)
	if (type == "AuthUser1") return new AuthUser1()
	else if (type == "AuthUser2") return new AuthUser2()
		.
		.
		.
		else if (type == "AuthUserN") return new AuthUserN() 
}
class User1
{
	private AuthUserSimpleFactory sfo
	public AuthUser requestAuthUser(string type)
	{
		AuthUser myAuthUser = sfo.createAuthUser(type)
		myAuthUser.register()
		return myAuthUser
	{	
}
.
.
.
class UserN
{
	private AuthUserSimpleFactory sfo
	public AuthUser requestAuthUser(string type)
	{
		AuthUser myAuthUser = sfo.createAuthUser(type)
		myAuthUser.register()
		return myAuthUser
	{	
}
abstract class AuthUser
{
	protected password, last_login, username, first_name, last_name, email, date_joined: string
	protected is_superuser, is_staff, is_active: int
	public void register()	
	{ }
}
class AuthUser1 extends AuthUser
{
	AuthUser1() //assign values entered by the user during registration
	{
		password = "password1"
		last_login = "last_login1"
		username = "username1"
		first_name = "first_name1"
		last_name = "last_name1"
		email = "email1"
		date_joined = "date_joined1"
		is_superuser = 0
		is_staff = 0
		is_active = 1
	}
	public void register()
	{ }
}
.
.
.
class AuthUserN extends AuthUser
{
	AuthUserN() //assign user entered values during registration
	{
		password = "passwordN"
		last_login = "last_loginN"
		username = "usernameN"
		first_name = "first_nameN"
		last_name = "last_nameN"
		email = "emailN"
		date_joined = "date_joinedN"
		is_superuser = 0
		is_staff = 0
		is_active = 1
	}
	public void register()
	{ }
}
\end{lstlisting}

\clearpage
\begin{figure}[h]
        \centering
        \includegraphics[width=0.8\textwidth]{FactoryForms.png}
        \caption{Forms Class}
\end{figure}

\begin{lstlisting}
class FormsSimpleFactory
{
	public forms createForms(string type)
	if (type == "Forms1") return new Forms1()
	else if (type == "Forms2") return new Forms2()
	.
	.
	.
		else if (type == "FormsN") return new FormsN()
}
class User1
{
	private FormsSimpleFactory sfo
	public forms submitForms(string type)
		{
			forms myForms = sfo.createForms(type)
			myForms.saveFormEditor()
			return myForms
		}
}
.
.
.
class UserN
{
	private FormsSimpleFactory sfo
	public forms submitForms(string type)
		{
			forms myForms = sfo.createForms(type)
			myForms.saveFormEditor()
			return myForms
		}
}
abstract class forms
{
	protected form_id, user_id, is_active: int
	protected title, description, created_at, updated_at, form_json: string
	public void saveFormEditor()
	{ }
}
class forms1 extends forms
{
	Forms1() //assign user entered values during form creation
	{
		form_id = 1
		user_id = 1
		is_active = 1
		title = "title1"
		description = "description1"
		created_at = "created_at1"
		updated_at = "updated_at1"
		form_json = "form_json1"
	}
	public void saveFormEditor()
	{ }
}
.
.
.
class formsN extends forms
{
	FormsN() //assign user entered values during form creation
	{
		form_id = N
		user_id = N
		is_active = N
		title = "title1"
		description = "description1"
		created_at = "created_at1"
		updated_at = "updated_at1"
		form_json = "form_json1"
	}
	public void saveFormEditor()
	{ }
}
\end{lstlisting}

\clearpage
\begin{figure}[h]
        \centering
        \includegraphics[width=0.8\textwidth]{FactoryResponses.png}
        \caption{Responses Class}
\end{figure}

\begin{lstlisting}
class ResponsesSimpleFactory
{
	public responses createResponses(string type)
	if (type == "Responses1") return new Responses1()
	else if (type == "Responses2") return new Responses2()
	.
	.
	.
		else if (type == "ResponsesN") return new ResponsesN()
}
class User1
{
	private ResponsesSimpleFactory sfo
	public responses createResponses(string type)
	{
		responses myResponses = sfo.createResponses(type)
		myResponses.saveResponses()
		return myResponses
	}
}
.
.
.
class UserN
{
	private ResponsesSimpleFactory sfo
	public responses createResponses(string type)
	{
		responses myResponses = sfo.createResponses(type)
		myResponses.saveResponses()
		return myResponses
	}
}
abstract class responses
{
	protected response_id, form_id, user_id: int
	protected response_json, created_at, updated_at: string
	public void saveResponses()
	{ }
}
class Responses1 extends responses
{
	Responses1() //assign values entered by the user during response creation
	{
		response_id = 1
		form_id = 1
		user_id = 1
		response_json = "response_json1"
		created_at = "created_at1"
		updated_at = "updated_at1"
	}
	public void saveResponses()
	{ }	
}
.
.
.
class ResponsesN extends responses
{
	ResponsesN() //assign values entered by the user during response creation
	{
		response_id = N
		form_id = N
		user_id = N
		response_json = "response_jsonN"
		created_at = "created_atN"
		updated_at = "updated_atN"
	}
	public void saveResponses()
	{ }	
}
\end{lstlisting}

\newpage
\subsection{Provide the class diagram of the whole system by incorporating the two design patterns.}

\begin{figure}[h]
        \centering
        \includegraphics[width=\textwidth]{entireClassDiagram.png}
        \caption{Whole System Class Diagram}
\end{figure}

\linebreak
    \hfill \break
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Software Construction}
\subsection{Submit the screenshot of the entire structure of the code within the web framework.}

\singlespacing
\begin{lstlisting}
    ├───dLocal
│   └───dLocal
│       │   db.sqlite3
│       │   manage.py
│       │   models.py
│       │
│       ├───CS476P
│       │   │   asgi.py
│       │   │   settings.py
│       │   │   urls.py
│       │   │   wsgi.py
│       │   │   __init__.py
│       │   │
│       │   └───__pycache__
│       │           settings.cpython-310.pyc
│       │           settings.cpython-311.pyc
│       │           urls.cpython-310.pyc
│       │           urls.cpython-311.pyc
│       │           wsgi.cpython-310.pyc
│       │           wsgi.cpython-311.pyc
│       │           __init__.cpython-310.pyc
│       │           __init__.cpython-311.pyc
│       │
│       ├───projects
│       │   │   admin.py
│       │   │   apps.py
│       │   │   models.py
│       │   │   tests.py
│       │   │   urls.py
│       │   │   views.py
│       │   │   __init__.py
│       │   │
│       │   ├───migrations
│       │   │   │   0001_initial.py
│       │   │   │   0002_tag_project_vote_ratio_project_vote_total_review_and_more.py
│       │   │   │   0003_form_project_featured_image_response.py
│       │   │   │   0004_project_owner.py
│       │   │   │   0005_alter_form_created.py
│       │   │   │   0005_rename_created_form_created_at_remove_form_id_and_more.py
│       │   │   │   0006_forms_projectsform.py
│       │   │   │   0006_rename_created_response_created_at_and_more.py
│       │   │   │   0007_merge_20230319_1823.py
│       │   │   │   __init__.py
│       │   │   │
│       │   │   └───__pycache__
│       │   │           0001_initial.cpython-310.pyc
│       │   │           0001_initial.cpython-311.pyc
│       │   │           0002_tag_project_vote_ratio_project_vote_total_review_and_more.cpython-310.pyc
│       │   │           0002_tag_project_vote_ratio_project_vote_total_review_and_more.cpython-311.pyc
│       │   │           0003_form_project_featured_image_response.cpython-310.pyc
│       │   │           0003_form_project_featured_image_response.cpython-311.pyc
│       │   │           0004_project_owner.cpython-310.pyc
│       │   │           0004_project_owner.cpython-311.pyc
│       │   │           0005_alter_form_created.cpython-310.pyc
│       │   │           0005_rename_created_form_created_at_remove_form_id_and_more.cpython-310.pyc
│       │   │           0006_forms_projectsform.cpython-310.pyc
│       │   │           0006_rename_created_response_created_at_and_more.cpython-310.pyc
│       │   │           0007_merge_20230319_1823.cpython-310.pyc
│       │   │           __init__.cpython-310.pyc
│       │   │           __init__.cpython-311.pyc
│       │   │
│       │   ├───templates
│       │   │   └───projects
│       │   │           formEditor.html
│       │   │           Home.html
│       │   │           results.html
│       │   │           saveFormEditor.html
│       │   │           Survey.html
│       │   │           Thanks.html
│       │   │
│       │   └───__pycache__
│       │           admin.cpython-310.pyc
│       │           admin.cpython-311.pyc
│       │           apps.cpython-310.pyc
│       │           apps.cpython-311.pyc
│       │           models.cpython-310.pyc
│       │           models.cpython-311.pyc
│       │           urls.cpython-310.pyc
│       │           urls.cpython-311.pyc
│       │           views.cpython-310.pyc
│       │           views.cpython-311.pyc
│       │           __init__.cpython-310.pyc
│       │           __init__.cpython-311.pyc
│       │
│       ├───static
│       │   ├───images
│       │   │   │   default.jpg
│       │   │   │   logo.png
│       │   │   │   thankyou.png
│       │   │   │
│       │   │   └───profiles
│       │   │           logo.jpg
│       │   │           user-default.png
│       │   │
│       │   ├───js
│       │   │       form.js
│       │   │       manager.js
│       │   │       survey.js
│       │   │       userForms.js
│       │   │
│       │   └───styles
│       │           formEditor.css
│       │           main.css
│       │           results_table.css
│       │
│       ├───staticfiles
│       │   ├───admin
│       │   │   ├───css
│       │   │   │   │   autocomplete.css
│       │   │   │   │   base.css
│       │   │   │   │   changelists.css
│       │   │   │   │   dark_mode.css
│       │   │   │   │   dashboard.css
│       │   │   │   │   fonts.css
│       │   │   │   │   forms.css
│       │   │   │   │   login.css
│       │   │   │   │   nav_sidebar.css
│       │   │   │   │   responsive.css
│       │   │   │   │   responsive_rtl.css
│       │   │   │   │   rtl.css
│       │   │   │   │   widgets.css
│       │   │   │   │
│       │   │   │   └───vendor
│       │   │   │       └───select2
│       │   │   │               LICENSE-SELECT2.md
│       │   │   │               select2.css
│       │   │   │               select2.min.css
│       │   │   │
│       │   │   ├───fonts
│       │   │   │       LICENSE.txt
│       │   │   │       README.txt
│       │   │   │       Roboto-Bold-webfont.woff
│       │   │   │       Roboto-Light-webfont.woff
│       │   │   │       Roboto-Regular-webfont.woff
│       │   │   │
│       │   │   ├───img
│       │   │   │   │   calendar-icons.svg
│       │   │   │   │   icon-addlink.svg
│       │   │   │   │   icon-alert.svg
│       │   │   │   │   icon-calendar.svg
│       │   │   │   │   icon-changelink.svg
│       │   │   │   │   icon-clock.svg
│       │   │   │   │   icon-deletelink.svg
│       │   │   │   │   icon-no.svg
│       │   │   │   │   icon-unknown-alt.svg
│       │   │   │   │   icon-unknown.svg
│       │   │   │   │   icon-viewlink.svg
│       │   │   │   │   icon-yes.svg
│       │   │   │   │   inline-delete.svg
│       │   │   │   │   LICENSE
│       │   │   │   │   README.txt
│       │   │   │   │   search.svg
│       │   │   │   │   selector-icons.svg
│       │   │   │   │   sorting-icons.svg
│       │   │   │   │   tooltag-add.svg
│       │   │   │   │   tooltag-arrowright.svg
│       │   │   │   │
│       │   │   │   └───gis
│       │   │   │           move_vertex_off.svg
│       │   │   │           move_vertex_on.svg
│       │   │   │
│       │   │   └───js
│       │   │       │   actions.js
│       │   │       │   autocomplete.js
│       │   │       │   calendar.js
│       │   │       │   cancel.js
│       │   │       │   change_form.js
│       │   │       │   collapse.js
│       │   │       │   core.js
│       │   │       │   filters.js
│       │   │       │   inlines.js
│       │   │       │   jquery.init.js
│       │   │       │   nav_sidebar.js
│       │   │       │   popup_response.js
│       │   │       │   prepopulate.js
│       │   │       │   prepopulate_init.js
│       │   │       │   SelectBox.js
│       │   │       │   SelectFilter2.js
│       │   │       │   urlify.js
│       │   │       │
│       │   │       ├───admin
│       │   │       │       DateTimeShortcuts.js
│       │   │       │       RelatedObjectLookups.js
│       │   │       │
│       │   │       └───vendor
│       │   │           ├───jquery
│       │   │           │       jquery.js
│       │   │           │       jquery.min.js
│       │   │           │       LICENSE.txt
│       │   │           │
│       │   │           ├───select2
│       │   │           │   │   LICENSE.md
│       │   │           │   │   select2.full.js
│       │   │           │   │   select2.full.min.js
│       │   │           │   │
│       │   │           │   └───i18n
│       │   │           │           af.js
│       │   │           │           ar.js
│       │   │           │           az.js
│       │   │           │           bg.js
│       │   │           │           bn.js
│       │   │           │           bs.js
│       │   │           │           ca.js
│       │   │           │           cs.js
│       │   │           │           da.js
│       │   │           │           de.js
│       │   │           │           dsb.js
│       │   │           │           el.js
│       │   │           │           en.js
│       │   │           │           es.js
│       │   │           │           et.js
│       │   │           │           eu.js
│       │   │           │           fa.js
│       │   │           │           fi.js
│       │   │           │           fr.js
│       │   │           │           gl.js
│       │   │           │           he.js
│       │   │           │           hi.js
│       │   │           │           hr.js
│       │   │           │           hsb.js
│       │   │           │           hu.js
│       │   │           │           hy.js
│       │   │           │           id.js
│       │   │           │           is.js
│       │   │           │           it.js
│       │   │           │           ja.js
│       │   │           │           ka.js
│       │   │           │           km.js
│       │   │           │           ko.js
│       │   │           │           lt.js
│       │   │           │           lv.js
│       │   │           │           mk.js
│       │   │           │           ms.js
│       │   │           │           nb.js
│       │   │           │           ne.js
│       │   │           │           nl.js
│       │   │           │           pl.js
│       │   │           │           ps.js
│       │   │           │           pt-BR.js
│       │   │           │           pt.js
│       │   │           │           ro.js
│       │   │           │           ru.js
│       │   │           │           sk.js
│       │   │           │           sl.js
│       │   │           │           sq.js
│       │   │           │           sr-Cyrl.js
│       │   │           │           sr.js
│       │   │           │           sv.js
│       │   │           │           th.js
│       │   │           │           tk.js
│       │   │           │           tr.js
│       │   │           │           uk.js
│       │   │           │           vi.js
│       │   │           │           zh-CN.js
│       │   │           │           zh-TW.js
│       │   │           │
│       │   │           └───xregexp
│       │   │                   LICENSE.txt
│       │   │                   xregexp.js
│       │   │                   xregexp.min.js
│       │   │
│       │   ├───images
│       │   │   │   default.jpg
│       │   │   │   logo.png
│       │   │   │   thankyou.png
│       │   │   │
│       │   │   └───profiles
│       │   │           logo.jpg
│       │   │           user-default.png
│       │   │
│       │   ├───js
│       │   │       form.js
│       │   │       manager.js
│       │   │       survey.js
│       │   │
│       │   └───styles
│       │           formEditor.css
│       │           main.css
│       │           results_table.css
│       │
│       ├───templates
│       │       file.vuerd.json
│       │       main.html
│       │       navbar.html
│       │
│       └───users
│           │   admin.py
│           │   apps.py
│           │   forms.py
│           │   models.py
│           │   tests.py
│           │   urls.py
│           │   views.py
│           │   __init__.py
│           │
│           ├───migrations
│           │   │   0001_initial.py
│           │   │   0002_profile_username.py
│           │   │   0003_profile_location_skill.py
│           │   │   __init__.py
│           │   │
│           │   └───__pycache__
│           │           0001_initial.cpython-310.pyc
│           │           0001_initial.cpython-311.pyc
│           │           0002_profile_username.cpython-310.pyc
│           │           0002_profile_username.cpython-311.pyc
│           │           0003_profile_location_skill.cpython-310.pyc
│           │           0003_profile_location_skill.cpython-311.pyc
│           │           __init__.cpython-310.pyc
│           │           __init__.cpython-311.pyc
│           │
│           ├───templates
│           │   └───users
│           │           formEditor-old.html
│           │           login_register.html
│           │           profiles.html
│           │
│           └───__pycache__
│                   admin.cpython-310.pyc
│                   admin.cpython-311.pyc
│                   apps.cpython-310.pyc
│                   apps.cpython-311.pyc
│                   forms.cpython-310.pyc
│                   forms.cpython-311.pyc
│                   models.cpython-310.pyc
│                   models.cpython-311.pyc
│                   urls.cpython-310.pyc
│                   urls.cpython-311.pyc
│                   views.cpython-310.pyc
│                   views.cpython-311.pyc
│                   __init__.cpython-310.pyc
│                   __init__.cpython-311.pyc
│
└───formEditorJS
        form.js
        index.html
\end{lstlisting}

\doublespacing

\begin{figure}[h]
        \centering
        \includegraphics[width=0.45\textwidth]{5a1.png}
        %\caption{Forms Class in Users Application and Project Application}
\end{figure}
\begin{figure}[h]
        \centering
        \includegraphics[width=0.45\textwidth]{5a2.png}
        %\caption{Forms Class in Users Application and Project Application}
\end{figure}
\begin{figure}[h]
        \centering
        \includegraphics[width=0.45\textwidth]{5a3.png}
        %\caption{Forms Class in Users Application and Project Application}
\end{figure}
\begin{figure}[h]
        \centering
        \includegraphics[width=0.45\textwidth]{5a4.png}
        %\caption{Forms Class in Users Application and Project Application}
\end{figure}
\begin{figure}[h]
        \centering
        \includegraphics[width=0.45\textwidth]{5a5.png}
        %\caption{Forms Class in Users Application and Project Application}
\end{figure}
\begin{figure}[h]
        \centering
        \includegraphics[width=0.45\textwidth]{5a6.png}
        %\caption{Forms Class in Users Application and Project Application}
\end{figure}

\linebreak
    \hfill \break
    \clearpage
\subsection{Deployment diagram regarding the hardware configuration of the code. Indicate the supported Web browsers, the application/Web servers and the database solution.}

All web browsers are supported. Our application is created using the Django framework and the web server is ngrok. MySQL was used as the database solution.

\begin{figure}[h]
        \centering
        \includegraphics[width=0.9\textwidth]{deploymentDiagram.png}
        %\caption{Forms Class in Users Application and Project Application}
\end{figure}

\linebreak
\clearpage    
\subsection{Screenshots of all table contents of the system data.}

\begin{figure}[h]
\centering
\includegraphics[width=0.95\textwidth]{5c1.png}
\end{figure}
\begin{figure}[h]
\centering
\includegraphics[width=0.95\textwidth]{5c2.png}
\end{figure}
\begin{figure}[h]
\centering
\includegraphics[width=0.95\textwidth]{5c3.png}
\end{figure}
\newpage

\linebreak
\subsection{GitHub link of the entire program. All students must contribute equally to the programming part. The commit log of each student will be checked within GitHub. Website builders, such as Wordpress, are not allowed.}
\linebreak
\url{https://github.com/zachary-huber/feedback-app}
\hfill \break

@@

\section{Acceptance Testing: select test cases for both user roles. The sign-in and sign-up are excluded from testing.}
\subsection{Correctness testing using four test cases (screenshots of both inputs and outputs).}
%\newline

\textbf{Feedback gatherer:}
\begin{itemize}
    \item[] Input: Feedback gatherer creates a survey by selecting the types of answers and entering the questions. 
    \begin{figure}[h]
        \centering
        \includegraphics[width=0.6\textwidth]{correct1.png}
        %\caption{Profile Class}
\end{figure}

Output: When they click the “Create Survey” button, a QR code is generated.
\begin{figure}[h]
        \centering
        \includegraphics[width=0.6\textwidth]{correct2.png}
        %\caption{Profile Class}
\end{figure}

Input: Feedback gatherer clicks on one of the past surveys.
\begin{figure}[h]
        \centering
        \includegraphics[width=0.6\textwidth]{correct3.png}
        %\caption{Profile Class}
\end{figure}

Output: Feedback gatherer can view the responses to the correct survey.
\begin{figure}[h]
        \centering
        \includegraphics[width=0.6\textwidth]{correct4.png}
        %\caption{Profile Class}
\end{figure}
\end{itemize}

\hfill \break
\clearpage
\textbf{Respondent:}
\begin{itemize}
    \item[] Input: Respondent scans the QR code.
    \begin{figure}[h]
        \centering
        \includegraphics[width=0.6\textwidth]{correct5.png}
        %\caption{Profile Class}
\end{figure}

    \item[] Output: Respondent is taken to the correct survey.
    \begin{figure}[h]
        \centering
        \includegraphics[width=0.6\textwidth]{correct6.png}
        %\caption{Profile Class}
\end{figure}
\clearpage
    \item[] Input: Respondent completes the survey and clicks submit.
    \begin{figure}[h]
        \centering
        \includegraphics[width=0.6\textwidth]{correct7.png}
        %\caption{Profile Class}
\end{figure}

    \item[] Output: Respondent is taken to the thank you page.
    \begin{figure}[h]
        \centering
        \includegraphics[width=0.6\textwidth]{correct8.png}
        %\caption{Profile Class}
\end{figure}
\end{itemize}

@@

\begin{itemize}
    \item[] Input: Feedback gatherer tries to go to the sign up page while already logged in.
    \begin{figure}[h]
        \centering
        \includegraphics[width=0.6\textwidth]{robust1.png}
        %\caption{Profile Class}
\end{figure}
\item[]

Output: Feedback gatherer is redirected to landing page.
\begin{figure}[h]
        \centering
        \includegraphics[width=0.6\textwidth]{robust2.png}
        %\caption{Profile Class}
\end{figure}

Input: Feedback gatherer tries to go to the login page while already logged in.
\begin{figure}[h]
        \centering
        \includegraphics[width=0.6\textwidth]{robust3.png}
        %\caption{Profile Class}
\end{figure}
\clearpage
Output: Feedback gatherer is redirected to landing page.
\begin{figure}[h]
        \centering
        \includegraphics[width=0.6\textwidth]{robust4.png}
        %\caption{Profile Class}
\end{figure}

\end{itemize}
\newline 
\hfill \break

\textbf{Respondent:}
\begin{itemize}
    \item[] Input: Respondent tries to go the landing page while not logged in.
    \begin{figure}[h]
        \centering
        \includegraphics[width=0.6\textwidth]{robust5.png}
        %\caption{Profile Class}
\end{figure}

Output: Respondent is redirected to login page.
\begin{figure}[h]
        \centering
        \includegraphics[width=0.6\textwidth]{robust6.png}
        %\caption{Profile Class}
\end{figure}
